---
title: "Assignment 1"
author: "Eun Ho Kim(12455415), Younjoo Mo (12475440)"
date: "6/5/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1
Before we start, we have to write three codes 


```{r}
library(tidyverse)
library(Ecdat)
data(Housing)
```

```{r Housing}
dim(Housing)
```
There exist 546 rows and 12 columns.

To check whether there exist some missing values,
```{r}
sum(is.na(Housing))
```

Therefore, there are no missing values

# Question 2
```{r}
boxplot(Housing$lotsize, main='Box plot of lotsize', horizontal=TRUE)

```

Here, we can find outliers on the right side of the box plot.

```{r}
a=ggplot(data=Housing, mapping=aes(x=lotsize))
a+geom_histogram(bins=20)+xlab('lotsize')
```

Here, we can find outliers on approximately 16,000


# Question 3

## Question a

Z score method
```{r}
Z_lotsize=(Housing$lotsize-mean(Housing$lotsize))/sd(Housing$lotsize)
```

By using Z-score, if Z score is bigger than 3 or smaller than -3, it is outlier!
```{r}
filter(Housing, Z_lotsize>3| Z_lotsize< -3)

```

## Question b
IQR method
```{r}
summary(Housing$lotsize)

```
Here, we can find Q1=3600 and Q3=6360.

By using IQR method, if lotsize is smaller than $Q1-(1.5*IQR)$ or bigger than 
$Q3+(1.5*IQR)$, it is an outlier.

```{r}
Q1=3600
Q3=6360
IQR=Q3-Q1
A=Q1-(1.5*IQR)
A
B=Q3+(1.5*IQR)
B
filter(Housing,lotsize< -540 | lotsize>10500)
```


# Question 4

## Question a

```{r}
summarise(Housing,
          mean_price=mean(price),
          median_price=median(price),
          sd_price=sd(price),
          mean_absolute_deviation_price=sum(abs(Housing$price-mean(Housing$price)))/nrow(Housing),
          IQR_price=quantile(Housing$price,0.75)-quantile(Housing$price,0.25),
          skewness_price=3*(mean(Housing$price)-median(Housing$price))/sd(Housing$price))

```


## Question b
```{r}
Z_price=(Housing$price-mean(Housing$price))/sd(Housing$price)
skewness_Z_price=3*(mean(Z_price)-median(Z_price))/(sd(Z_price))
skewness_price=3*(mean(Housing$price)-median(Housing$price))/(sd(Housing$price))
```

```{r}
skewness_Z_price
```

```{r}
skewness_price
```

The skewness of price and z scores are same. 
It implies that Z score does not change skewness.

# Question 5

## Question a
```{r}
qqnorm(Housing$price)
qqline(Housing$price, col='red')
```


## Question b

From 5-a, we found out that housing prices are not normally distributed using a normal Q-Q plot. 
In order to achieve normality, 
we tried 

Z_score normalization
```{r}
qqnorm(Z_price)
qqline(Z_price, col='blue')
```



min-max normalization
```{r}
price_min_max=(Housing$price-min(Housing$price))/(max(Housing$price)-min(Housing$price))
qqnorm(price_min_max)
qqline(price_min_max, col='green')

```


log normalization
```{r}
qqnorm(log(Housing$price))
qqline(log(Housing$price),col='purple')

```

root X ($\sqrt{X}$) transformation method

```{r}
qqnorm(sqrt(Housing$price))
qqline(sqrt(Housing$price),col='orange')
```

$\frac{1}{\sqrt{x}}$ transformation method

```{r}
qqnorm(1/sqrt(Housing$price))
qqline(1/sqrt(Housing$price),col='yellow')
```

As a result, we can analyze graphs by using QQ plot interpretation. 
Log normalization makes observations most likely fall onto a qqline, which means that the data comes from a normal population.

# Question 6

## Question a
```{r}
Housing$bedrooms_dummy=1*(Housing$bedrooms>'3')

```


```{r}
mutate(Housing,bedrooms_dummy)

```

## Question b
```{r}
filter(Housing,bedrooms_dummy==1, prefarea=='yes' )

```


## Question c
```{r}
mean_average_price=mean(Housing$price)
mean_price_dummy1_prefareaYes=mean(filter(Housing,bedrooms_dummy==1, prefarea=='yes' )$price)
mean_average_price
mean_price_dummy1_prefareaYes

```

Average price of housing with more than 3 bedrooms and located in the preferred neighborhood of the city are much more expensive than average houses.

# Question 7

## Question a
```{r}
(max(Housing$lotsize)-min(Housing$lotsize))/3


Housing$lotsize_bin_equal_width=cut_width(Housing$lotsize, width=4850)
head(Housing$lotsize_bin_equal_width)
table(Housing$lotsize_bin_equal_width)
```


## Question b
```{r}
Housing$lotsize_bin_equal_freq=cut_number(Housing$lotsize,n=4)
table(Housing$lotsize_bin_equal_freq)

```


