---
title: "Life Insurance Mathematics: Assignment 1"
author: 
- Hyunkyun Chung(12527742), Jagathiswarra Rao Raja Rao(12542660)
- Younjoo Mo(12475440), Thomas Rigny(12914347)
date: '6 September 2020'
output: pdf_document
---
Q2.
With all the given information, we can calculate the yearly loan payments from t=0 to t=23 as follows:
```{r}
loans <- c(10000, 20000, 30000, rep(0, 20))
payments <- c(rep(0,3), 1, cumprod(0.95*rep(1,19)))
interest <- c(rep(0.06, 5), rep(0.07, 5), rep(0.08, 12))
yearly_discount_factor <- (1+interest)^(-1)
discount_factors <- c(1, cumprod(yearly_discount_factor))

pv_payments <- payments * discount_factors
pv_loans <- loans * discount_factors 

k1 <- sum(pv_loans)/sum(pv_payments)

k <- k1 * payments
k
```


Q3 a.
Since there is no mention about compounding of interest rate, we examine two different cases: non-compounding and monthly compounding.
First, if the interest is not compounding,
```{r}
i<-0.055
r1<-i/12
number_payment<-15*12
payment<-c(0, rep(1,number_payment))
discount_factor<-(1+r1)^(-(0:number_payment))
PV_payment<-payment*discount_factor
K<-150000/sum(PV_payment); K
```
The monthly payments should be $1225.625, so it matches the result from Bloomberg Mortgage Calculator.

If the interest is monthly compounding,
```{r}
i<-0.055
r2<-(1+i)^(1/12)-1
number_payment<-15*12
payment<-c(0, rep(1,number_payment))
discount_factor<-(1+r2)^(-(0:number_payment))
PV_payment<-payment*discount_factor
K<-150000/sum(PV_payment); K
```
we have a different result, $1214.988.

Q3 b.
Here, we examine the two cases again. Also, since the first payment date is set as Sepember in the provided benchmark, we follow the same timeline.

With non-compounding interest rate, we get:
```{r}
library(FinancialMath)
amortization<-amort.table(Loan=150000, n=number_payment, i=r1)
amort<-data.frame(amortization$Schedule)
x<-4
year<-1
while(x<=180){
  cat("The balance at the end of year", year, "=", amort[x, 4], "\n")
  year<-year+1
  x<-x+12
  }
```
It shows the result just as same as the benchmark. Therefore, if the given annual interest rate is meant to be non-compounding, the Bloomberg Mortgage Calculator is indeed correct.

Now we examine the second case with monthly compounding interest rate.
```{r}
amortization<-amort.table(Loan=150000, n=number_payment, i=r2)
amort<-data.frame(amortization$Schedule)
x<-4
year<-1
while(x<=180){
  cat("The balance at the end of year", year, "=", amort[x, 4], "\n")
  year<-year+1
  x<-x+12
}
```
As expected, we have a different results than those from the benchmark.